A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-07-03 docs/methods/erosion_methods.tex
Addressed Reviewer 1

To numerically compute the completed double-layer potential~\eqref{eqn:completed_BIE}, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.  Then, $N = MN_\iin + N_\out$ is the total number of discretization points of $\bd\Omega$.  The double-layer potential in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
\begin{align}
  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
      \Delta s_{j}\, , \quad i=1,\ldots,N \, ,
  \label{eqn:trapDLP}
\end{align}
where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
$\xx_j$, and
\begin{align}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \, ,
\end{align}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is replaced with the limiting value of the double-layer potential
\begin{align}
  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)) \, ,
\end{align}
where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent vector at $\xx \in \bd\Omega$.  The equations for the Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are also discretized with the trapezoid rule.  Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
\begin{subequations}
  \label{eqn:completed_BIE_discretized}
  \begin{align}
  \label{eqn:discretized_DLP}
    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) +
      \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) \\
    \llambda_\ell &= \sum_{\xx_j \in \gamma_\ell} \eeta(\xx_j) 
      \Delta s_j \, , \\ 
    \xi_\ell &= \sum_{\xx_j \in \gamma_\ell}
      {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j \, ,
  \end{align}
\end{subequations}
for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  When $\xx_i \in \Gamma$, the term 
\begin{align}
  \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
      \nn(\xx_j))\eeta(\xx_j) \, ,
\end{align}
is added to~\eqref{eqn:discretized_DLP}.  Since we discretize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Post processing quantities of interest}
\label{s:qoi}
We further characterize the flow by computing the vorticity (Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}), and drag (Section~\ref{sec:drag}).  Once equation~\eqref{eqn:completed_DLP} is solved, the vorticity and pressure will be computed at points both inside the fluid bulk and on the along individual bodies, and then the drag of individual bodies will be computed.  For target points in the fluid domain, the integrands of the layer potentials are periodic and smooth, and the trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.  However, if the target point is close to $\bd \Omega$, a nearly-singular integrand must be integrated, and this requires upsampling that is described in Section~\ref{sec:NSI}.  When the target points is on the boundary, the integrands involve singularities that are evaluated by combining singularity subtraction and odd-even integration~\cite{sid-isr1988}.

>>>>

To numerically compute the completed double-layer potential~\eqref{eqn:completed_BIE}, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.  Then, $N = MN_\iin + N_\out$ is the total number of discretization points of $\bd\Omega$.  The double-layer potential in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
\begin{align}
  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
      \Delta s_{j}\, , \quad i=1,\ldots,N \, ,
  \label{eqn:trapDLP}
\end{align}
where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
$\xx_j$, and
\begin{align}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \, ,
\end{align}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is replaced with the limiting value of the double-layer potential
\begin{align}
  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)) \, ,
\end{align}
where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent vector at $\xx \in \bd\Omega$.  The equations for the Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are also discretized with the trapezoid rule.  Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
\begin{subequations}
  \label{eqn:completed_BIE_discretized}
  \begin{align}
  \label{eqn:discretized_DLP}
    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) +
      \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) \\
    \llambda_\ell &= \sum_{\xx_j \in \gamma_\ell} \eeta(\xx_j) 
      \Delta s_j \, , \\ 
    \xi_\ell &= \sum_{\xx_j \in \gamma_\ell}
      {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j \, ,
  \end{align}
\end{subequations}
for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  When $\xx_i \in \Gamma$, the term 
\begin{align}
  \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
      \nn(\xx_j))\eeta(\xx_j) \Delta s_j \, ,
\end{align}
is added to~\eqref{eqn:discretized_DLP}.  Since we discretize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Post processing quantities of interest}
\label{s:qoi}
We further characterize the flow by computing the vorticity
(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
and drag (Section~\ref{sec:drag}).  Once
equation~\eqref{eqn:completed_DLP} is solved for the velocity, $\uu =
(u,v)$, the vorticity and pressure will be computed at points both
inside the fluid bulk and on the along individual bodies, and then the
drag of individual bodies will be computed.  For target points in the
fluid domain, the integrands of the layer potentials are periodic and
smooth, and the trapezoid rule guarantees spectral
accuracy~\cite{tre-wei2014}.  However, if the target point is close to
$\bd \Omega$, a nearly-singular integrand must be integrated, and this
requires upsampling that is described in Section~\ref{sec:NSI}.  When
the target points is on the boundary, the integrands involve
singularities that are evaluated by combining singularity subtraction
and odd-even integration~\cite{sid-isr1988}.
